\pagestyle{empty}
\pagecolor{pink!30}

\breaksection*{\centering{DRAFT REPORT --- VERSION 3}}

\boxreview{Latest Revision: \today~at~\currenttime \\ \textit{This is a draft report for internal review} \\ The chapters beyond the Scenario Storylines chapter are in the first draft stage and are undergoing continual development.}

\vspace{-1em}

\boxblack{CHANGE LOG}{
    New in version 3:
    \begin{itemize}
        \item Revised the scenario storylines and methodology chapters based on internal review.
        \item Added the quantification chapter, which is not in the first draft stage.
        \item This chapter includes detailled descriptions of the scenario parameters and, in the case of the external elements, their quantification.
        \item Internal elements will be quantified using a bottom-up approach whereby waste streams interpret the scenario parameters through correlations with their product groups. This will be discussed at the next workshop.
    \end{itemize}
}

\boxmagenta{CONTRIBUTING}{
    Please contribute to the work on the scenario work in the following ways:
    \begin{itemize}
        \item In a CSV file with the format: `name, line start, line end, comment, reference' (if reference is applicable, please provide the DOI or BibTeX).
        \item Please use consistent formatting for the page numbers and any referencing.
        \item FutuRaM members add their comments to the shared document found at \href{https://weeeforum.sharepoint.com/:x:/s/futuram/EdTouKTiLoZDt3Li142aYuQBp9ubxI_T8hiYquDFPyd4-A?e=vSOI3F}{this link \faLink}.
        \item The same template can be downloaded from \href{https://futuram-project.github.io/FutuRaM.github.io/WP2/WP2.1_ScenarioStorylines_Review.xlsx}{here \faLink} and sent to \href{mailto:s.c.mcdowall@cml.leidenuniv.nl}{SCM \faEnvelopeSquare} for inclusion in the shared document.
        \item You can also contribute directly to the \textsf{\LaTeX} source files on the \href{https://github.com/FutuRaM-Project/WP2/tree/main/2.1}{WP2 GitHub repository \faGithub}.
    \end{itemize}
}

\vspace{-1em}

\boxws{Waste Streams, please check your sections \\
    \begin{itemize}
        \item Review the waste stream impact sections for each scenario        
        \item Add more references, especially for the targets, regulations, and projections.
        \item Contribute to the main points raised by the reviewers of the first drafts (see below).
        \item Read the quantification chapter and develop your plan to interpret the scenarios in your waste stream.
        \item Consider how the scenario parameters and your waste stream model codebase will interface.
        \item Consider how your waste stream model will interface with the integrated model.
    \end{itemize}
}

\vspace{-1em}

\boxgreen{QUANTIFICATION}{
    \begin{itemize}
        \item Read the quantification chapter and develop your plan to interpret the scenarios in your waste stream.
        \item Consider how the scenario parameters and your waste stream model codebase will interface.
        \item Consider how your waste stream model will interface with the integrated model.
        \item Contribute to the data collection in the future technology and product list \href{https://shorturl.at/gxMO8}{here \faLink}.
    \end{itemize}
        }
\vspace{-1em}

\boxblue{DISCUSSION POINTS}{
    \begin{itemize}
        \item How to transfer general targets into product-specific values?
        \item[] \textit{general CRM/SRM $\rightarrow$ waste streams $\rightarrow$ product groups}
        \item[] \hspace{2em}\textit{We would need a set of constraints for each of the recovery flows and processes, as well as the individual waste flows (by code) in each WS, to backcast this.}
        \item Consideration of possible future resource constraints in the scenarios.
        \item [] \textit{We suggest covering this in sensitivity analysis and multi-objective-optimisation.}
        \item Economic considerations (prices, subsidies, PPP vs. GPD etc.).
        \item Geopolitical Considerations (supply risk, trade, etc.).
        \item Scenarios relationship with the United Nations Framework Classification (UNFC).
        \item Choice of background energy scenario (i.e. STEP from the IEA)
    \end{itemize}
}

\vspace{-1em}

\boxblack{SOME LINKS}{
    \begin{itemize}
    
        \item Quantification: \autoref{chapter:quantification}
        \item Appendices: \autoref{chapter:appendices}
        \item WP2 folder on the FutuRaM Sharepoint See \href{https://shorturl.at/wLNS2}{\faLink} for more details.
    \end{itemize}
}

\clearpage
