\breaksection{Internal elements --- Technological Change}\label{sec:quantification_internal_rec}
\subsection{Introduction}

\boxgreen{\textbf{Technological Change}}{
        \textbf{Scenario elements}
        \begin{itemize}
          \item \textbf{Product technology (composition)} 
          \item \textbf{Recovery technology} 
          \item \textbf{Recovery system development}
        \end{itemize}
        \textbf{Waste model parameters include:}
        \begin{itemize}
          \item \textbf{Lifetimes:} \\ function of product technology
          \item \textbf{Composition:} \\ function of product composition, durability, design-for-repair, etc.
        \end{itemize}
        \textbf{Recovery model parameters include:}
        \begin{itemize}
          \item \textbf{Recovery processes:}\\  market penetration of recovery technologies
          \item \textbf{Transfer coefficients:} \\ function of recovery technologies
          \item \textbf{Recovery system size:} \\ BAU - set by trends in BAU, CIR \& REC - defined by model outcomes within constraints
        \end{itemize}
          }

        Product technology and recovery technology development will differ across scenarios and across product groups in each waste stream. These differences must be integrated into individual stock-flow models through interpretations of the scenarios and the conversion of these into estimations of the changes. 
        
        recognising the need for assumptions about technological advancements in products and recovery processes.  The document stresses the importance of addressing product technology development until 2050, as this will vary in importance across different waste streams.
          
        \subsection{Methodology}
          
        \begin{enumerate}
          \item \textbf{Scenario Analysis:}\newline
          Different future scenarios are explored to understand how technological development might unfold. This includes examining existing and new technologies, their properties over time, and how they are diffused into the market.
          
          \item \textbf{Waste Stream Focus:}\newline
          The approach varies in importance across different waste streams like EEE, ELV, BATT, CDW, and SLASH. For each stream, specific assumptions and approaches need to be tailored.
          
          \item \textbf{Data Collection:}\newline
          Gathering data from various sources, including patents, scientific publications, business reports, and expert opinions, to inform assumptions about technology development.
          
          \item \textbf{Modelling Approach:}\newline
          Utilizing dynamic Material Flow Analysis (dMFA) for modelling, covering a timeline from 2000 to 2050. This includes historical data analysis and future projections based on assumptions.
          
          \item \textbf{Technology Diffusion:}\newline
          Understanding the rate and manner in which technologies gain market share, depicted through S-curves. This involves considering factors like price, legislation, and organizational support.
          
          \item \textbf{Assumptions on Technology Development:}\newline
          Outlining specific assumptions at the level of each waste stream and aligning these assumptions across streams where possible.
          
          \item \textbf{Integration into SF Models:}\newline
          Incorporating the assumptions about product and recovery technology development into SF models to reflect the scenario-based variations.
          
          \item \textbf{Transparency and Communication:}\newline
          Ensuring that the chosen approaches and assumptions are clearly stated for transparency and ease of understanding.
      \end{enumerate}
      
      The methodology is designed to provide a comprehensive understanding of how future technology developments can impact various aspects of waste management and resource recovery in a circular economy context.
      

% table: the main technological scenario elements

% DOMAIN	ELEMENT	INTERNAL	EXTERNAL	OUTSIDE	BAU	REC	CIR	MODEL PARAMETERS AFFECTED
% ECO	Subsidies and taxation to promote recovery strategies	✔			I	III	I	recycling rates, recovery capacity, recovery impacts, collection
% POL	Targets and enforcement to promote recovery strategies	✔			I	III	I	recycling rates, recovery rates, capacity
% TECH	Product technology	✔			I	III	III	lifetimes, recovery rates, recovery impacts
% TECH	Recovery technology	✔			I	III	III	recovery rates, recovery capacity, recovery impacts
% TECH	Integration of SRM recovery system across Europe	✔			I	III	III	recycling rates, recovery rates, recovery capacity, recovery impacts

\clearpage

\subsection{Summary}

\boxreview{This summary will be compiled once the individual waste stream sections for each parameter are complete.}

\clearpage

% pull in the other subsections
\input{133a-quantification_rec_tech-product_description}
\clearpage
\input{133a-quantification_rec_tech-product_scenarios}

\input{133b-quantification_rec_tech-recovery_description}
\clearpage
\input{133b-quantification_rec_tech-recovery_scenarios}
\clearpage
% \input{133c-quantification_rec_system_description}
% \clearpage
% \input{133c-quantification_rec_system_scenarios}

% template for including new subsections
% \input{133x-quantification_rec_Y_description}
% \input{133x-quantification_rec_Y_scenarios}

\subsubsection{Conclusion}


\boxreview{This conclusion will be compiled once the individual waste stream sections for each parameter are complete.}


\sectionEndlines
\clearpage
